Mixed language processing increases cross-language phonetic transfer in Bengali-English Bilinguals

### 2021-05-25 draft_glossa-psych/glossa-psych_AM-ID_manuscript.tex
r code addtions

\author[Auromita \& Indranil]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
{%as many authors as you like, each separated by \AND.
  \spauthor{Auromita Mitra\\ 
  \institute{The EFL University}\\
  \small{%105, Bd. Raspail, 75005 Paris\\
  auromita.mitra@gmail.com}
  }
  \AND
  \spauthor{Indranil Dutta \\
  \institute{Jadavpur University}\\
  \small{%Warmoesberg 26, 1000 Brussel\\
  indranildutta.lnl@jadavpuruniversity.in}
  }%
}
%\usepackage{gb4e}
\begin{document}

>>>>

% \author[Auromita \& Indranil]% short form of the author names for the running header. If no short author is given, no authors print in the headers.
% {%as many authors as you like, each separated by \AND.
%   \spauthor{Auromita Mitra\\ 
%   \institute{The EFL University}\\
%   \small{%105, Bd. Raspail, 75005 Paris\\
%   auromita.mitra@gmail.com}
%   }
%   \AND
%   \spauthor{Indranil Dutta \\
%   \institute{Jadavpur University}\\
%   \small{%Warmoesberg 26, 1000 Brussel\\
%   indranildutta.lnl@jadavpuruniversity.in}
%   }%
% }
%\usepackage{gb4e}
\begin{document}
